---
title: "Replication of Processing bound-variable singular they by Chung-Hye Han & Keir Moulton (2022, Canadian Journal of Linguistics)"
author: "Katherine Johnson (katiej23@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    toc: true
    toc_depth: 3
---

```{r include=F}
## Libraries 
library(tidyverse)
library(pwr)
library(readxl)    
library(ordinal)   
library(emmeans)   
library(osfr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(tidyr)
library(lme4)
library(purrr)
library(scales) # For pretty percentage labels on the graph
library(lmerTest)
library(readr)
```

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

## Introduction

<!-- [No abstract is needed.]  Each replication project will have a straightforward, no frills report of the study and results.  These reports will be publicly available as supplementary material for the aggregate report(s) of the project as a whole.  Also, to maximize project integrity, the intro and methods will be written and critiqued in advance of data collection.  Introductions can be just 1-2 paragraphs clarifying the main idea of the original study, the target finding for replication, and any other essential information.  It will NOT have a literature review -- that is in the original publication. You can write both the introduction and the methods in past tense.   -->

This experiment replicated work from Han and Moulton (2022) on the processing of singular *they*. In previous work (e.g., Conrod 2019), bound-variable singular *they* (1) was found to be rated as more acceptable than referential singular *they* (2).

(1) Bound *they*: Every child loves their mother.

(2) Referential *they*: My friend's child loves their mother.

Han and Moulton (2022) built on this work, exploring the relationship between bound vs. referential singular *they* and gender specificity of the antecedent as it relates to ease of processing a sentence. They found that bound-variable singular *they* with a gendered antecedent has a processing advantage over both referential singular *they* and bound-variable singular *they* without a gendered antecedent.

This experiment replicated the sentence processing experiment that Han and Moulton ran (their experiment 1b), aiming to (dis)confirm their observed interaction between bound-variable vs. referential singular *they* and gender specificity of the antecedent, as well as introducing an additional type of antecedent that Han and Moulton did not consider, shown below:

(3) Referential and named *they*: Alex loves their mother.


## Methods

### Power Analysis

<!-- Original effect size, power analysis for samples to achieve 80%, 90%, 95% power to detect that effect size.  Considerations of feasibility for selecting planned sample size. -->

Han&Moulton report a t-value of 2.34 (p. 285) with 193 participants considered in their calculations. The Cohen's d is estimated as $d = \frac{t}{\sqrt{n}} = \frac{2.34}{\sqrt{193}} = 0.168$. From this, we can estimate power:

```{r}
power_result <- pwr.t.test(
  d = 0.168,                 # Effect size (Cohen's d)
  sig.level = 0.05,
  power = 0.80,
  type = "paired",           # Every participant saw all the conditions (across different items)
  alternative = "two.sided"
)
plot(power_result)
```

### Planned Sample

<!-- Planned sample size and/or termination rule, sampling frame, known demographics if any, preselection rules if any. -->

The results of the power analysis suggest that at least 281 participants should be included in this replication. I propose collecting data from 300 people to be conservative and to allow exclusions of participants with low scores on comprehension questions.

### Materials

<!-- All materials - can quote directly from original article - just put the text in quotations and note that this was followed precisely.  Or, quote directly and just point out exceptions to what was described in the original article. -->

The original experiment materials cross 'two two-level factors, Antecedent (QUANT vs. REF) and Pronoun (THEY vs. HE), yielding four experimental conditions' (Han&Moulton 2022, 283). This replication introduces a third level in the Antecedent factor (QUANT vs. REF vs. NAMED), yielding six total experimental conditions. 'The test sentences in [this experiment] were made to be [long] so that the sentences do not end with the target region containing the critical pronoun. Also, the definite description in the embedded specificational clause began with the one who to ensure a singular interpretation of the post-copula pronoun.' (Han&Moulton 2022, 283).

(5) Only one competitor could win the race.
a. Every competitor thought that they one who would win the race would be them when the times were finally announced. QUANT.THEY

b. Every competitor that that the one who would win the race would be him when the times were finally announced. QUANT.HE

c. The youngest competitor that that the one who would win the race would be them when the times were finally announced. REF.THEY

d. The youngest competitor that that the one who would win the race would be him when the times were finally announced. REF.HE

e. Avery thought that the one who would win the race would be them when the times were finally announced. NAMED.THEY

f. Avery thought that the one who would win the race would be him when the times were finally announced. NAMED.HE

(Adapted from Han&Moulton 2022, (13))

### Procedure	

<!-- Can quote directly from original article - just put the text in quotations and note that this was followed precisely.  Or, quote directly and just point out exceptions to what was described in the original article. -->

300 native English users participated in this study online via Prolific. Participants self-reported to be native users of English in their demographics on Prolific. Each participant received $3.20 as compensation upon completion of the experiment. Thirty item sets like (5) were distributed over six lists in a Latin-square design. `In addition, each list contained a set of [30] fillers. The sentences were presented on [Prolific] in a uniquely generated random order for each participant, using the moving-window paradigm (Just et al. 1982). After reading the context sentence, participants advanced to the next region by pressing on the space bar. No region could be displayed more than once. After each experimental sentence was read, a comprehension question was presented, which could be answered by pressing one key for ‘yes’ or another key for ‘no’. The comprehension questions tested participants’ understanding of the sentence, but not their interpretation of the critical pronoun. The comprehension question for the item in [(5)] is in [(6)]'. (Adapted from Han and Moulton 2022, 283-284)

(6) Was there going to be a winner of a race? (Han&Moulton 2022, (14))

### Analysis Plan

<!-- Can also quote directly, though it is less often spelled out effectively for an analysis strategy section.  The key is to report an analysis strategy that is as close to the original - data cleaning rules, data exclusion rules, covariates, etc. - as possible.   -->

Participants with low comprehension question response score (<50%\footnote{This value was eventually changed to 75% in subsequent analysis; see justification below.}) and extremely fast reading speed per region (<50ms) were excluded. Additionally, reading times of a region that were 10 standard deviations above the mean were removed, in order to exclude extreme outliers from analysis. The regions of analysis are Region 7 (the target region), Region 8 (the spillover region), and Region 9. We calculated RRTs using character length from the entire dataset (including fillers) to estimate the reading time for each region for each participant (Ferreira and Clifton 1986, Trueswell and Tanenhaus 1994, Phillips 2006). We analyzed each region’s RRTs with a mixed model, with a random-effects
structure: RRT ∼ Antecedent \* Pronoun + (1+Antecedent \* Pronoun|Participant) + (1+Antecedent\*Pronoun|Item). (Adapted from Han&Moulton 2022, p. 284).

My addition to this experiment -- exploring three different types of antecedent instead of two -- does not require any changes to the analysis conducted in the original experiment.

<!-- **Clarify key analysis of interest here**  You can also pre-specify additional analyses you plan to do. -->

### Differences from Original Study

<!-- Explicitly describe known differences in sample, setting, procedure, and analysis plan from original study.  The goal, of course, is to minimize those differences, but differences will inevitably occur.  Also, note whether such differences are anticipated to make a difference based on claims in the original article or subsequent published research on the conditions for obtaining the effect. -->

The sample size of the replication is larger than the original study (300 participants vs. 193 participants), following the justification outlined above. The setting is similar: the replication is conducted online via Prolific, while the original study recruited participants via Amazon Mechnical Turk and directed them to the experiment on Ibex Farm. The procedure is comparable, although different numbers of critical and filler trials were included because of the additional variation that my replication explores. The original experiment included 20 critical trials (5 per condition) and 40 filler trials; my replication includes 30 critical trials (5 per condition) and 30 filler trials (number of filler trials was decreased to save money by making the experiment slightly shorter). None of these changes are expected to affect results, although the additional critical conditions of course introduce additional data to be analyzed (with the analysis plan exactly matching the plan for the rest of the data).

### Methods Addendum (Post Data Collection)

<!-- You can comment this section out prior to final report with data collection. -->


```{r include=F}
# Get participant demographics

demo_raw <- read_csv("./participant-demographics/prolific_demographic_export_6a14e1cf1b78e1520c7ffd5b.csv")

avg_age <- demo_raw %>%
  pull(Age) %>%             # Use pull() to extract the column as a vector
  parse_number() %>%        # Converts "25" to 25 and handles non-numeric chars
  mean(na.rm = TRUE)        # Ignores missing values

max_age <- demo_raw %>%
  pull(Age) %>%             # Use pull() to extract the column as a vector
  parse_number() %>%        # Converts "25" to 25 and handles non-numeric chars
  max(na.rm = TRUE)        # Ignores missing values

min_age <- demo_raw %>%
  pull(Age) %>%             # Use pull() to extract the column as a vector
  parse_number() %>%        # Converts "25" to 25 and handles non-numeric chars
  min(na.rm = TRUE)        # Ignores missing values
```

```{r include=F}
# Collect all the data from the experiment

# Create a list of the file paths for all the CSVs
local_files <- list.files(path = "./data/", pattern = "\\.csv$", full.names = TRUE)

# Filter out files without enough columns. These are data from earlier pilots where less information was collected.

# Define the exact number of columns a complete file should have
EXPECTED_COLS <- 24

count_columns <- function(file_path) {
  headers <- suppressMessages(read_csv(file_path, n_max = 0, show_col_types = FALSE))
  return(ncol(headers))
}

file_col_counts <- map_int(local_files, count_columns)

# Filter files to only include the ones with the expected columns
valid_files <- local_files[file_col_counts == EXPECTED_COLS]

# Calculate and print the summary statistics
total_starting_files <- length(local_files)
total_kept_files <- length(valid_files)
total_excluded_files <- total_starting_files - total_kept_files

# message("--- Data Loading Summary ---")
# message("Total files found: ", total_starting_files)
# message("Files excluded (incorrect column count): ", total_excluded_files)
# message("Files kept for analysis: ", total_kept_files)
# message("----------------------------")
# # ---------------------------------------------------------

# Read and combine only the valid files
rt_raw <- read_csv(valid_files, id = "file_name")
```

```{r include=F}
# Filter out participants who consented before a certain date. These are participants from pilot versions of the experiment rather than from the full study.

cutoff_time <- ymd_hms("2026-05-25 12:00:00", tz = "UTC")

# Look for the rows that actually have the timestamp, filter them, 
# and extract a unique list of their file names.
valid_participants <- rt_raw %>%
  filter(consent_timestamp >= cutoff_time) %>%
  pull(file_name) %>%
  unique()

# Keep ALL rows (even the ones with NA in the timestamp column) 
# as long as they belong to a file_name in the valid list
rt_sub_clean <- rt_raw %>%
  filter(file_name %in% valid_participants) %>%
  mutate(rt = as.numeric(rt)) # Force RT to be a number


# # Optional: See how many participants were kept vs dropped
# message(sprintf("Kept %d participants. Dropped %d participants.",
#                 length(valid_participants),
#                 length(unique(rt_raw$file_name)) - length(valid_participants)))
# 
# # Inspect the 15 earliest participants that SURVIVED the filter
# earliest_kept <- rt_sub_clean %>%
#   filter(!is.na(consent_timestamp)) %>%      # 1. Ignore all the trial rows with NA
#   select(file_name, consent_timestamp) %>%   # 2. Keep only the ID and timestamp columns
#   arrange(consent_timestamp) %>%             # 3. Sort chronologically (oldest first)
#   head(15)                                   # 4. Grab the top 15
# 
# # Print the result to the console
# print(earliest_kept)
```

```{r include=F}
# Now, I want to filter out participants with low comprehension question score and too-fast reading speed

# ==============================================================================
# 1. Participant-Level Exclusions (Separated for reporting)
# ==============================================================================
total_n <- n_distinct(rt_sub_clean$participant_id)

# A. Accuracy Exclusions (< 75%)
acc_summary <- rt_sub_clean %>%
  group_by(participant_id) %>%
  summarize(accuracy = mean(correct, na.rm = TRUE), .groups = "drop")

failed_acc_ids <- acc_summary %>%
  filter(accuracy < 0.75 | is.na(accuracy)) %>%
  pull(participant_id)

n_excluded_acc <- length(failed_acc_ids)

# B. Speed Exclusions (< 50ms)
# We filter out the accuracy failures first so we don't double-count participants
speed_summary <- rt_sub_clean %>%
  filter(!participant_id %in% failed_acc_ids) %>%
  filter(!is.na(condition)) %>% # Only check experimental trials for baseline speed
  group_by(participant_id) %>%
  summarize(mean_rt = mean(rt, na.rm = TRUE), .groups = "drop")

failed_speed_ids <- speed_summary %>%
  filter(mean_rt < 50 | is.na(mean_rt)) %>%
  pull(participant_id)

n_excluded_speed <- length(failed_speed_ids)

# C. Apply Participant Exclusions
rt_participant_filtered <- rt_sub_clean %>%
  filter(!participant_id %in% c(failed_acc_ids, failed_speed_ids))

kept_n <- n_distinct(rt_participant_filtered$participant_id)

# ==============================================================================
# 2. Trial-Level Exclusions (10 SD) and RRT Calculation
# ==============================================================================
trials_before <- nrow(rt_participant_filtered)

rt_clean <- rt_participant_filtered %>%
  group_by(participant_id) %>%
  # Remove 10 SD outliers
  filter(is.na(rt) | rt <= (mean(rt, na.rm = TRUE) + 10 * sd(rt, na.rm = TRUE))) %>%
  # Calculate word length and RRT
  mutate(word_length = nchar(word)) %>%
  mutate(RRT = as.numeric(residuals(lm(rt ~ word_length, na.action = na.exclude)))) %>%
  ungroup()

trials_after <- nrow(rt_clean)
trials_dropped <- trials_before - trials_after
pct_trials_dropped <- (trials_dropped / trials_before ) *100

# Print a clean summary to your console
cat("--- PARTICIPANT EXCLUSIONS ---\n")
cat("Starting Participants:", total_n, "\n")
cat("Excluded for Accuracy (< 75%):", n_excluded_acc, "\n")
cat("Excluded for Speed (< 50ms):", n_excluded_speed, "\n")
cat("Final Participants Kept:", kept_n, "\n\n")

cat("--- TRIAL EXCLUSIONS ---\n")
cat("Total trials before 10 SD trim:", trials_before, "\n")
cat("Total trials after 10 SD trim:", trials_after, "\n")
cat("Individual trials dropped:", trials_dropped, "\n")
```


#### Actual Sample
  <!-- Sample size, demographics, data exclusions based on rules spelled out in analysis plan. -->
```{r}
# At this point, my data should look like H&M's raw data.
# Now I want to figure out who to exclude for low question comprehension

# 1. Calculate each participant's total accuracy just once
participant_accuracies <- rt_sub_clean %>%
  group_by(participant_id) %>%
  summarize(accuracy = mean(correct, na.rm = TRUE))

# 2. Define the range of thresholds to test
# This creates a list from 0 to 1 (0% to 100%) stepping by 1%
thresholds_to_test <- seq(0, 1, by = 0.01)

# 3. Calculate how many people get excluded at EACH threshold
exclusion_curve <- tibble(threshold = thresholds_to_test) %>%
  mutate(
    # map_dbl runs the calculation for every single threshold in the list
    excluded_count = map_dbl(threshold, ~ sum(participant_accuracies$accuracy < .x))
  )

# 4. Plot the curve!
ggplot(exclusion_curve, aes(x = threshold, y = excluded_count)) +
  geom_line(color = "#2C3E50", size = 1.2) +
  
  # Add reference lines
  geom_vline(xintercept = 0.50, linetype = "dashed", color = "gray50") +
  annotate("text", x = 0.50, y = max(exclusion_curve$excluded_count) * 0.8, 
           label = "50% (Original)", angle = 90, vjust = -1, color = "gray50") +
  
  geom_vline(xintercept = 0.60, linetype = "dashed", color = "blue") +
  annotate("text", x = 0.60, y = max(exclusion_curve$excluded_count) * 0.8, 
           label = "60%", angle = 90, vjust = -1, color = "blue") +
  
  geom_vline(xintercept = 0.75, linetype = "dashed", color = "red") +
  annotate("text", x = 0.75, y = max(exclusion_curve$excluded_count) * 0.8, 
           label = "75%", angle = 90, vjust = -1, color = "red") +
  
  # Formatting
scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.1)) +  theme_minimal() +
  labs(
    title = "Robustness Check: Participant Exclusions by Accuracy Threshold",
    x = "Accuracy Threshold (Excluding < X%)",
    y = "Number of Participants Excluded"
  )
```
  
  303 participants were recruited on Prolific.\footnote{An apparent Prolific glitch led to collection of data from 303 rather than the intended 300 participants, and these additional data were included in analysis.} All participants were native English speakers, as reported in their Prolific demographics. The age of the participants ranges from `r min_age`-`r max_age`, with the mean age at `r round(avg_age, digits = 2)`. Participants who did not meet threshold accuracy on comprehension questions were excluded. The accuracy threshold was read off of the above plot, with 75% accuracy chosen as a reasonable threshold. This exclusion resulted in the exclusion of `r round(n_excluded_acc, digits = 2)` participants. Participants were also checked for an unreasonably fast reading speed per region (<50ms), although no participants met this exclusion criterion. Finally, reading times of a region that were 10 standard deviations above the mean were removed, in order to exclude extreme outliers from analysis. This resulted in excluding `r round(pct_trials_dropped, digits = 2)`% of the observations from the data.

#### Differences from pre-data collection methods plan
  <!-- Any differences from what was described as the original plan, or “none”. -->
The original analysis plan suggested modeling the data with the following model: RRT ∼ Antecedent \* Pronoun + (1+Antecedent \* Pronoun|Participant) + (1+Antecedent\*Pronoun|Item). However, such a model was found to have a singular fit on all regions that it was applied to, and the following simpler model was used instead: RRT ~ Antecedent \* Pronoun + (1 | Participant) + (1 | Item). This was the maximal model that converged.


## Results


### Data preparation

Data preparation following the analysis plan.
	
```{r include=F}
### Data Preparation

#### Load Relevant Libraries and Functions

#### Import data

#### Data exclusion / filtering

#### Prepare data for analysis - create columns etc.

## ^ Instructions from original template


```



```{r}
# Identify regions using string detection in 'stimulus'
rt_model <- rt_clean %>%
  filter(condition %in% c("quantificational_they", "specific_they", "named_they", 
                          "quantificational_he", "specific_he", "named_he")) %>%
  group_by(participant_id, item) %>%
  mutate(
    # Find the word_index where the stimulus CONTAINS our target words
    is_pronoun_region = str_detect(stimulus, regex("them|him", ignore_case = TRUE)),
    
    # Grab the index number for that specific row
    # We use min() just in case the detection triggers twice in one trial
    pron_idx = if(any(is_pronoun_region)) min(word_index[is_pronoun_region]) else NA_real_,
    
    # Define the three regions based on that index
    region_label = case_when(
      word_index == pron_idx ~ "1_Critical",
      word_index == pron_idx + 1 ~ "2_Spillover_1",
      word_index == pron_idx + 2 ~ "3_Spillover_2",
      TRUE ~ NA_character_
    )
  ) %>%
  # Filter to keep only our three regions
  filter(!is.na(region_label)) %>%
  ungroup()

# Add columns specifying Antecedent and Pronoun (i.e., separating these two from one another)
rt_model <- rt_model %>%
  separate(
    col = condition, 
    into = c("Antecedent", "Pronoun"), 
    sep = "_", 
    remove = FALSE # Optional, but highly recommended!
  )

# 3. Check the results
# print(paste("Rows found:", nrow(rt_model)))
# table(rt_model$region_label, rt_model$condition)
```


```{r}
# Gemini suggested that I should use "sum coding" instead of standard dummy coding because that's more likely to be what H&M used? I'm skeptical, but I'm trying it out
# 1. First, ensure R knows these columns are categorical factors
rt_model$Pronoun <- as.factor(rt_model$Pronoun)
rt_model$Antecedent <- as.factor(rt_model$Antecedent)

# 2. Apply the Sum Coding
# The number inside the parentheses is exactly how many levels that factor has
contrasts(rt_model$Pronoun) <- contr.sum(2)
contrasts(rt_model$Antecedent) <- contr.sum(3)

# 3. Optional: Verify that it worked!
# This should print a little matrix with 1s and -1s instead of 0s and 1s.
# contrasts(rt_model$Pronoun)
```

Copy the model from the paper:

```{r}
# The below complete random models get singular fits, so I remove interactions until I get a proper result
# # 1. Critical Region Model
# model_critical <- lmer(RRT ~ Antecedent * Pronoun + 
#                          (1 + Antecedent*Pronoun | participant_id) + 
#                          (1 + Antecedent*Pronoun | item), 
#                        data = filter(rt_model, region_label == "1_Critical"))
# 
# # 2. Spillover 1 Model
# model_spillover1 <- lmer(RRT ~ Antecedent * Pronoun + 
#                            (1 + Antecedent*Pronoun | participant_id) + 
#                            (1 + Antecedent*Pronoun | item), 
#                          data = filter(rt_model, region_label == "2_Spillover_1"))
# 
# # 3. Spillover 2 Model
# model_spillover2 <- lmer(RRT ~ Antecedent * Pronoun + 
#                            (1 + Antecedent*Pronoun | participant_id) + 
#                            (1 + Antecedent*Pronoun | item), 
#                          data = filter(rt_model, region_label == "3_Spillover_2"))

# 1. Critical Region Model
model_critical <- lmer(RRT ~ Antecedent * Pronoun + 
                         (1 | participant_id) + 
                         (1 | item), 
                       data = filter(rt_model, region_label == "1_Critical"))

# 2. Spillover 1 Model
model_spillover1 <- lmer(RRT ~ Antecedent * Pronoun + 
                           (1 | participant_id) + 
                           (1 | item), 
                         data = filter(rt_model, region_label == "2_Spillover_1"))

# 3. Spillover 2 Model
model_spillover2 <- lmer(RRT ~ Antecedent * Pronoun + 
                           (1 | participant_id) + 
                           (1 | item), 
                         data = filter(rt_model, region_label == "3_Spillover_2"))
```

```{r}
anova(model_critical, type="III")
anova(model_spillover1, type="III")
anova(model_spillover2, type="III")
```



```{r}
# This is for the plotting
rt_summary <- rt_model %>%
  group_by(Antecedent, Pronoun, region_label) %>%
  summarize(
    mean_rt = mean(rt, na.rm = TRUE),
    se = sd(rt, na.rm = TRUE) / sqrt(n()),
    
    mean_RRT = mean(RRT, na.rm = TRUE),
    se_RRT = sd(RRT, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# Fix the labels for the x-axis
rt_summary$region_label <- factor(rt_summary$region_label, 
                                    levels = c("1_Critical", "2_Spillover_1", "3_Spillover_2"),
                                    labels = c("Critical", "Spillover 1", "Spillover 2"))
```

Here I want to replicate H\&M's table 3: RRT by condition for all regions. I want 6 rows: quant by pronoun, spec by pronoun, and named (my new data) by pronoun

```{r}
# Transform the tibble into the desired table format
final_table <- rt_summary %>%
  # 1. Create two combined string columns: one for raw RT, one for RRT
  mutate(
    RT = sprintf("%.0f (%.0f)", mean_rt, se),
    RRT = sprintf("%.0f (%.0f)", mean_RRT, se_RRT) # Kept at 2 decimals for residuals
  ) %>%
  
  # 2. Select our grouping variables, the region label, and our TWO new combined columns
  select(Antecedent, Pronoun, region_label, RT, RRT) %>%
  
  # 3. Pivot the data to wide format
  # By providing a vector of column names to values_from, R will automatically
  # create 6 columns (e.g., RT_critical, RRT_critical, RT_spillover 1...)
  pivot_wider(
    names_from = region_label,
    values_from = c(RT, RRT)
  ) %>%
  
  # 4. Re-order the rows based on your custom theoretical hierarchy
  mutate(
    Antecedent = factor(Antecedent, levels = c("quantificational", "specific", "named")),
    Pronoun = factor(Pronoun, levels = c("they", "he"))
  ) %>%
  arrange(Antecedent, Pronoun)

# View the final result
print(final_table)
```

```{r}
# Can remove named data to create a plot more similar to H&M's original
rt_summary_wo_named <- rt_summary %>%
  filter(Antecedent %in% c("quantificational", "specific"))

# The Plot
ggplot(rt_summary, aes(x = region_label, y = mean_RRT, 
                         color = Antecedent, shape = Pronoun, 
                         group = interaction(Antecedent, Pronoun))) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_RRT - se_RRT, ymax = mean_RRT + se_RRT), width = 0.1) +
  scale_x_discrete(labels = c("Critical" = "Region 7\n(them/him when)", 
                              "Spillover 1" = "Region 8\n(the times)", 
                              "Spillover 2" = "Region 9\n(were finally)")) +
  labs(title = "Mean RRTs by condition",
       x = "",
       y = "RRT") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~Antecedent)
```


### Confirmatory analysis

The analyses as specified in the analysis plan.  

*Side-by-side graph with original graph is ideal here*

### Exploratory analyses

Any follow-up analyses desired (not required).  

## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.
